Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-08-25 Paperfolder/MDPI_submission/Revision01/MDPI_submission/Paperfolder.tex
updated respnses and revision and diff files

%=================================================================
\documentclass[nutrients,article,submitted,moreauthors,pdftex]{Definitions/mdpi}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Public Health, Aichi Medical University
School of Medicine, Nagakute, Japan; \\
$^{2}$ \quad Departmet of Public Health, Fujita Health University School
of Medicine, Toyoake, Japan; \\
$^{3}$ \quad Public Health, Department of Social Medicine, Osaka
University Graduate School of Medicine, Osaka, Japan; \\
$^{4}$ \quad Department of Public Health, Hokkaido University, Graduate
School of Medicine, Sapporo, Japan; \\
}
% Contact information of the corresponding author
\corres{Correspondence: Email.:
\href{mailto:chaochen@wangcc.me}{\nolinkurl{chaochen@wangcc.me}}; Tel.:
+81-561-62-3311. Department of Public Health, Aichi Medical University
School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan
(C.W.)}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{The aim was to further examine the relationship between milk
intake and stroke mortality among the Japanese population. We used data
from the Japan Collaborative Cohort (JACC) Study to estimate the
posterior acceleration factors (AF) as well as the hazard ratios (HR)
comparing individuals with different milk intake frequencies against
those who never consumed milk at the study baseline. These estimations
were computed through a series of Bayesian survival models that employed
a Markov Chain Monte Carlo simulation process. 100000 posterior samples
for each individual were generated separately through four independent
chains after model convergency were confirmed. Posterior probabilites
that daily milk consumers had lower hazard or delayed mortality from
strokes compared to non-consumers was 99.0\% and 78.0\% for men and
women, respectively. Accordingly, the estimated posterior means of AF
and HR for daily milk consumers were 0.88 (95\% Credible Interval, CrI:
0.81, 0.96) and 0.80 (95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI:
0.88, 1.10) and 0.95 (95\% CrI: 0.80, 1.17) for women. In conclusion,
data from the JACC study has provided strong evidence that daily milk
intake among Japanese men was associated with delayed and lower hazard
of mortality from stroke especially cerebral infarction.}

@@

Eastern Asian populations were reported to have higher burden from
either mortality or morbidity from stroke than populations in European
or American regions \citep{Kim2014}. Dairy food, especially milk has
been suggested to reduce stroke risk by nearly 7\% for each 200 g
increment of daily consumption \citep{DeGoede2016}. Although 2 daily
servings of milk or dairy products is recommended in Japan
\citep{Yoshiike2007}, the actual per capita intake (\(\approx\) 63
g/day) of these food groups is much lower and less frequent than that in
Western countries \citep{Saito2019}. Given that previous reports have
also indicated no significant
\citep{Iso1999, sauvaget2003intake, Elwood2004} or even positive
associations \citep{Larsson2009}, whether people with such a low level
intake of milk can still benefit against stroke would require
elucidation. A more intuitive interpretation would be available if we
were able to show the probabilities and how certain the existing data
can provide evidence about whether drinking milk can delay or lower the
hazard of dying from stroke. Accelerated failure time models under
Bayesian framework are convenient tools that would help avoid worrying
about the assumption of proportional hazard normally required in a Cox
proportional hazard model and can directly show how faster/slower
individuals in one exposure group might have an event compared to others
among different exposure groups \citep{Wei1992, ibrahim2014b}.

Our aim was to provide a more straightforward answer to the primary
research question that whether someone answered he/she drank milk at the
baseline of study had lower hazard of dying from stroke compared with
his/her counterparts who said they never consumed milk. If the answer to
the primary objective was yes, then the probabilities that individuals
with different frequencies of milk intake may had lower hazard compared
with those who never drank milk were calculated through a Markov Chain
Monte Carlo (MCMC) simulation process. A Bayesian survival analysis
method was applied on an existing database and through which, we also
provided estimates about whether drinking milk could delay a stroke
mortality event from happening after controlling for the other potential
confounders.

@@

We used data from the Japan Collaborative Cohort (JACC) study, which was
sponsored by the Ministry of Education, Sports, Science, and Technology
of Japan. Sampling methods and details about the JACC study have been
described extensively in the literature
\citep{Ohno2001, Tamakoshi2005, Tamakoshi2013}. Participants of the JACC
study completed self-administered questionnaires about their lifestyles,
food intake (food frequency questionnaire, FFQ), and medical histories
of cardiovascular disease or cancer. In the final follow-up of the JACC
study, data from a total of 110585 individuals (46395 men and 64190
women) were successfully retained for the current analysis. We further
excluded samples if they meet one of the following criteria: 1) with any
disease history of stroke, cancer, myocardial infarction, ischemic heart
disease, or other types heart disease (n = 6655, 2931 men and 3724
women); 2) did not answer the question regarding their milk consumption
in the baseline FFQ survey (n = 9545, 3593 men and 5952 women). Finally,
94385 (39386 men and 54999 women) are left in the database. The study
design and informed consent procedure were approved by the Ethics Review
Committee of Hokkaido University School of Medicine.

@@

Frequency of milk intake during the preceding year of the baseline was
assessed by FFQ from ``never'', ``1-2 times/month'', ``1-2 times/week'',
``3-4 times/week'', and ``Almost daily''. The exact amount of milk
consumption was difficult to assess here. However, good reproducibility
and validity were confirmed previously (Spearman rank correlation
coefficient between milk intake frequency and weighed dietary record for
12 days was 0.65) \citep{Date2005}.

The causes and date of death were obtained from death certificates and
were systematically reviewed. The follow-up period was defined as from
the time of the baseline survey was completed, which was between
1988-1990, until the end of 2009 (administrative censor), or the date
when move-out of study area, or the date of death from stroke recorded,
whichever occurred first. Other causes of death were treated as censored
and assumed not informative. The causes of death were coded by the 10th
Revision of the International Statistical Classification of Diseases and
Related Health Problems (ICD-10), therefore stroke was defined as
I60-I69. We further classified these deaths into hemorrhagic stroke
(I60, I61 and I62) or cerebral infarction (I63) when subtypes of stroke
in their death certificates were available.

@@

We calculated sex-specific means (standard deviation, sd) and proportion
of selected baseline characteristics according to the frequency of milk
intake. Age-adjusted stroke mortality rate were expressed as per 1000
person-year predicted through poisson regression models.

@@

The total follow-up was 1555073 person-years (median = 19.3 years),
during which 2675 death from stroke was confirmed (1352 men and 1323
women). Among these stroke mortality, 952 were hemorrhagic stroke (432
men and 520 women), and 957 were cerebral infarction (520 men and 437
women). Age-adjusted stroke mortality rates for each category of milk
intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000
person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for
women.

@@

Detailed results from the Bayesian survival models (crude, age-adjusted
and multivariable-adjusted) according to the frequency of milk intake
separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and
\textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
milk, both men and women had slower speed and lower hazard of dying from
total stroke in crude models. Velocities that milk consumers dying from
stroke is slower by a crude acceleration factor (AF) between 0.79 (sd =
0.05; 95\% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95\% CrI: 0.85, 1.02)
compared with non-consumers. Chances that the posterior crude HRs were
estimated to be lower than 1 for those who had at least 1-2 times/month
was higher than 86.5\% in men and greater than 94.6\% in women. However,
lower hazard and delayed time-to-event was observed to remain after age
or multivariable adjustment only among daily male milk consumers.
Specifically, the mean (sd; 95\% CrI) of posterior
multivariable-adjusted AF and HR for daily male consumers of milk were
0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95\% CrI:
0.69, 0.93) with a probability of 99.0\% to be smaller than the null
value (=1). Daily female milk consumers had posterior AFs and HRs that
were distributed with means of 0.97 (sd = 0.09; 95\% CrI: 0.88, 1.10)
and 0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\% of
chance that their HRs could be smaller than 1.

@@

These findings are in line with our previous report
\citep{wang_milk_2015} as well as other studies conducted in East Asian
populations
\citep{umesawa2008dietary, kondo2013consumption, ozawa2017dietary, sauvaget2003intake, Talaei_2016}.
Moreover, we have further updated with more comprehensive and
straightforward evidence about whether and how certain the data had
shown about daily consumption of milk is contributing to a postponed
stroke (mostly cerebral infarction) mortality event among Japanese men.
A recent dose-response meta-analysis of 18 prospective cohort studies
had also shown a similar negative association \citep{DeGoede2016}
between milk consumption and risk of stroke. The same meta-analysis also
reported a greater reduction of risk of stroke (18\%) for East Asian
population in contrast with the 7\% less risk in the pooled overall
finding for all populations combined. Benefits of increased milk intake
might be particularly noticeable in East Asian countries where strokes
are relatively more common, and milk consumption is much lower than
those studies conducted among European or American populations
\citep{dehghan2018association}.

@@

Some limitations here are worth mentioning. First, the milk intake
frequency as well as other lifestyle information was collected only once
at the baseline and was self-reported. Apparently life habits are
possible to alter over time and these would resulted in misclassfication
and residual confoundings. Second, despite reasonable validity of FFQ in
the JACC study cohort was assessed and confirmed, measurement errors are
inevitable. Therefore, we did not try to compute the amount of
consumption by multiplying an average volume per occasion with the
frequency of intake since the random error might be exaggerated and the
observed associations may have attenuated. Strengths of our analyses
included that we have transformed the research questions to more
transparent ones that is easier for interpretation. Direct probabilities
that daily milk intake is associated with lower hazard or delayed stroke
mortality event were provided here after thorough computer simulations.

>>>>

%=================================================================
\documentclass[nutrients,article,submitted,moreauthors,pdftex]{mdpi}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Public Health, Aichi Medical University
School of Medicine, Nagakute, Japan; \\
$^{2}$ \quad Departmet of Public Health, Fujita Health University School
of Medicine, Toyoake, Japan; \\
$^{3}$ \quad Public Health, Department of Social Medicine, Osaka
University Graduate School of Medicine, Osaka, Japan; \\
$^{4}$ \quad Department of Public Health, Hokkaido University, Faculty
of Medicine, Sapporo, Japan; \\
}
% Contact information of the corresponding author
\corres{Correspondence: Email.:
\href{mailto:chaochen@wangcc.me}{\nolinkurl{chaochen@wangcc.me}}; Tel.:
+81-561-62-3311. Department of Public Health, Aichi Medical University
School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan
(C.W.)}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{The aim was to further examine the relationship between milk
intake and stroke mortality among the Japanese population. We used data
from the Japan Collaborative Cohort (JACC) Study (total number of
participants = 110585, age range: 40-79) to estimate the posterior
acceleration factors (AF) as well as the hazard ratios (HR) comparing
individuals with different milk intake frequencies against those who
never consumed milk at the study baseline. These estimations were
computed through a series of Bayesian survival models that employed a
Markov Chain Monte Carlo simulation process. 100000 posterior samples
were generated separately through four independent chains after model
convergency were confirmed. Posterior probabilites that daily milk
consumers had lower hazard or delayed mortality from strokes compared to
non-consumers was 99.0\% and 78.0\% for men and women, respectively.
Accordingly, the estimated posterior means of AF and HR for daily milk
consumers were 0.88 (95\% Credible Interval, CrI: 0.81, 0.96) and 0.80
(95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI: 0.88, 1.10) and 0.95
(95\% CrI: 0.80, 1.17) for women. In conclusion, data from the JACC
study has provided strong evidence that daily milk intake among Japanese
men was associated with delayed and lower hazard of mortality from
stroke especially cerebral infarction.}

@@

Eastern Asian populations were reported to have higher burden from
either mortality or morbidity from stroke than populations in European
or American regions \citep{Kim2014}. Dairy food, especially milk has
been suggested to reduce stroke risk by nearly 7\% for each 200 g
increment of daily consumption \citep{DeGoede2016}. Although 2 daily
servings of milk or dairy products is recommended in Japan
\citep{Yoshiike2007}, the actual per capita intake (\(\approx\) 63
g/day) of these food groups is much lower and less frequent than that in
Western countries \citep{Saito2019}. Given that previous reports have
also indicated no significant
\citep{Iso1999, sauvaget2003intake, Elwood2004} or even positive
associations \citep{Larsson2009}, it would be of interest to provide
information on the association within a context that most individuals
have much lower range of milk intake compared to most of the previous
studies. Whether people with such a low level intake of milk can still
benefit against stroke would require elucidation.

Moreover, a more intuitive interpretation would be available if we were
able to show the probabilities and how certain the existing data can
provide evidence about whether drinking milk can delay or lower the
hazard of dying from stroke. This would require transformation of the
research questions into ``Do individuals with milk intake habit have
lower hazard of dying from a stroke event compared with people who never
consume milk?'' Another way of asking the same research question would
be ``Can a event of dying from stroke be postponed by having a milk
intake habit?'' The later question is indeed directly comparing the
length of times before events or the speed from the same departure point
(entry of the study) to a fatal stroke event. Accelerated failure time
models (AFT) under Bayesian framework are convenient tools that would
help avoid worrying about the assumptions of repeatability of a large
scale prospective study, and can calculate the exact proportion of
posterior estimates (a hazard ratio) that is lower than 1. AFT model is
helpful in estimating acceleration factors which can be interpreted as
the speed for developing an event of interest. This speed parameter
shows how faster/slower individuals in one exposure group might have an
event compared to others among different exposure groups
\citep{Wei1992, ibrahim2014b}.

Our aim was to provide a more straightforward answer to the primary
research question that whether someone answered he/she drank milk at the
baseline of study had lower hazard of dying from stroke compared with
his/her counterparts who said they never consumed milk. If the answer to
the primary objective was yes, then the probabilities that individuals
with different frequencies of milk intake may had lower hazard compared
with those who never drank milk were calculated through a Markov Chain
Monte Carlo (MCMC) simulation process. A Bayesian survival analysis
method was applied on an existing database and through which, we
provided estimates about whether drinking milk could delay a stroke
mortality event from happening after controlling for the other potential
confounders.

@@

We used data from the Japan Collaborative Cohort (JACC) study, which was
sponsored by the Ministry of Education, Sports, Science, and Technology
of Japan. Sampling methods and details about the JACC study have been
described extensively in the literature
\citep{Ohno2001, Tamakoshi2005, Tamakoshi2013}. Participants of the JACC
study completed self-administered questionnaires about their lifestyles,
food intake (food frequency questionnaire, FFQ), and medical histories
of cardiovascular disease or cancer. In the final follow-up of the JACC
study, data from a total of 110585 individuals (46395 men and 64190
women) who aged between 40-79 at the baseline year were successfully
retained for the current analysis. We further excluded samples if they
meet one of the following criteria: 1) with any disease history of
stroke, cancer, myocardial infarction, ischemic heart disease, or other
types heart disease (n = 6655, 2931 men and 3724 women); 2) did not
answer the question regarding their milk consumption in the baseline FFQ
survey (n = 9545, 3593 men and 5952 women). Finally, 94385 (39386 men
and 54999 women) are left in the database. The study design and informed
consent procedure were approved by the Ethics Review Committee of
Hokkaido University School of Medicine.

@@

Frequency of milk intake during the preceding year of the baseline was
assessed by FFQ from ``never'', ``1-2 times/month'', ``1-2 times/week'',
``3-4 times/week'', and ``Almost daily''. The exact amount of milk
consumption was difficult to assess here. However, good reproducibility
and validity were confirmed previously (Spearman rank correlation
coefficient between milk intake frequency and weighed dietary record for
12 days was 0.65) \citep{Date2005}. From the same validation study
\citep{Date2005} on the FFQ, daily consumers of milk was found to have a
median intake of 146 gram per day. In the baseline year of the JACC
study (between 1988 and 1990), most ``milk and dairy product''
consumption (92.1\%) was in the form of whole milk \citep{eigyogenjyo}.

In the study area, investigators conducted systematic review of death
certificates till the end of 2009. Date and cause of death were
confirmed with the permission of the Director-General of the Prime
Minister's Office. The follow-up period was defined as from the time of
the baseline survey was completed, which was between 1988-1990, until
the end of 2009 (administrative censor), or the date when move-out of
study area, or the date of death from stroke recorded, whichever
occurred first. Other causes of death were treated as censored and
assumed not informative. The causes of death were coded by the 10th
Revision of the International Statistical Classification of Diseases and
Related Health Problems (ICD-10), therefore stroke was defined as
I60-I69. We further classified these deaths into hemorrhagic stroke
(I60, I61 and I62) or cerebral infarction (I63) when subtypes of stroke
in their death certificates were available.

@@

Analyses were stratified by sex as difference in milk consumption levels
and mortality rate was suggested previously
\citep{wang_milk_2015, Talaei_2016}. We calculated sex-specific means
(standard deviation, sd) and proportion of selected baseline
characteristics according to the frequency of milk intake. Age-adjusted
stroke mortality rate were expressed as per 1000 person-year predicted
through poisson regression models.

@@

The total follow-up was 1555073 person-years (median = 19.3 years),
during which 2675 deaths from stroke were confirmed (1352 men and 1323
women). Among these stroke mortality, 952 were hemorrhagic stroke (432
men and 520 women), and 957 were cerebral infarction (520 men and 437
women). Number of deaths from causes other than stroke were 18868 (10731
men and 8137 women); 5493 (2022 men and 3471 women) dropped out from the
follow-up (5.8\%); 67349 (25281 men and 42068 women) were censored at
the end of follow-up (71.4\%). The median (interquartile range, IQR) of
follow-up years for hemorrhagic stroke mortality were 9.9 (5.4, 12.3) in
men and 10.9 (5.9, 15.1) in women; the median (IQR) of follow-up years
for cerebral infarction mortality were 11.2 (7.1, 15.3) and 11.8 (7.9,
16.4) in men and women. Age-adjusted stroke mortality rates for each
category of milk intake frequency was estimated to be 1.8, 2.0, 1.7,
1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per
1000 person-year for women.

@@

Detailed results from the Bayesian survival models (crude, age-adjusted
and multivariable-adjusted) according to the frequency of milk intake
separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and
\textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
milk, both men and women had slower speed and lower hazard of dying from
total stroke in crude models. Velocities that milk consumers dying from
stroke is slower by a crude acceleration factor (AF) between 0.79 (sd =
0.05; 95\% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95\% CrI: 0.85, 1.02)
compared with non-consumers. Chances that the posterior crude HRs were
estimated to be lower than 1 for those who had at least 1-2 times/month
was higher than 86.5\% in men and greater than 94.6\% in women. However,
lower hazard and delayed time-to-event was observed to remain after age
or multivariable adjustment only among daily male

@@

\noindent milk consumers. Specifically, the mean (sd; 95\% CrI) of
posterior multivariable-adjusted AF and HR for daily male consumers of
milk were 0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (sd = 0.07;
95\% CrI: 0.69, 0.93) with a probability of 99.0\% to be smaller than
the null value (=1). Daily female milk consumers had posterior AFs and
HRs that were distributed with means of 0.97 (sd = 0.09; 95\% CrI: 0.88,
1.10) and 0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\%
of chance that their HRs could be smaller than 1.

These findings showed similar negative effect estimates reported
previously \citep{wang_milk_2015} using data from the same cohort, in
which the outcomes of interests were focused on cardiovascular diseases
and all-cause mortality. Moreover, we have further updated the results
with more comprehensive and straightforward evidence about whether and
how certain the data had shown about daily consumption of milk is
contributing to a postponed stroke (mostly cerebral infarction)
mortality event among Japanese men. A recent dose-response meta-analysis
of 18 prospective cohort studies had shown a similar negative
association \citep{DeGoede2016} between milk consumption and risk of
stroke. The same meta-analysis also reported a greater reduction of risk
of stroke (18\%) for East Asian population in contrast with the 7\% less
risk in the pooled overall finding for all populations combined.
Benefits of increased milk intake might be particularly noticeable in
East Asian countries where strokes are relatively more common, and milk
consumption is much lower than those studies conducted among European or
American populations \citep{dehghan2018association}. However, the Life
Span Study \citep{sauvaget2003intake}, which was conducted about 10
years earlier than the JACC Study, reported null association between
milk intake and fatal stroke among men and women combined who survived
from the Hiroshima and Nagasaki atomic bomb. The difference could be
largely explained by the different targeting populations between the two
studies. \citet{kondo2013consumption} also reported null association in
either men or women from the NIPPON DATA80 study. In fact, the exact
number of stroke mortality events was about 85\% less and the number of
participants in the NIPPON DATA80 was about 90\% less than those in the
JACC study database, their null association might likely due to its
limited statistical power. \citet{umesawa2008dietary} reported that
dairy calcium intake was inversely associated with ischemic stroke
mortality risk which could be considered as one of the potential
evidence that supported our findings. Furthermore, stronger inverse
association between milk consumption and stroke mortality in men rather
than in women was found in the Singapore Chinese Health Study
\citep{Talaei_2016} as well. The reasons for this gender differences is
currently unknown. It might be contributed by generally better/healthier
lifestyles (much less smokers and alcohol drinkers) in women regardless
of milk intake frequency, or maybe due to other factors that was not
available in/considered by our models such as intake of calcium
supplements. The probably existing beneficial effect by milk intake is
probably less evident in women than that in men. Further investigation
is needed.

@@

\hypertarget{strength-and-limitations}{%
\subsection{Strength and limitations}\label{strength-and-limitations}}

Some limitations here are worth mentioning. First, the milk intake
frequency as well as other lifestyle information was collected only once
at the baseline and was self-reported. Apparently life habits are
possible to alter over time and these would result in misclassfication
and residual confoundings. Second, despite reasonable validity of FFQ in
the JACC study cohort was assessed and confirmed, measurement errors are
inevitable. Therefore, we did not try to compute the amount of
consumption by multiplying an average volume per occasion with the
frequency of intake since the random error might be exaggerated and the
observed associations may have attenuated. Third, the Bayesian way of
conducting the survival analysis using a large sample size is
computationally expensive. However, the classic maximum likelihood
estimations are based on unrealistic assumptions such as repeatability
of the study and fixed but unknown values of parameters which are
unfulfilled in a large cohort study in the current setting. Strengths of
our analyses included that we have transformed the research questions to
more transparent ones that is easier for interpretation. Direct
probabilities that daily milk intake is associated with lower hazard or
delayed stroke mortality event were provided here after thorough
computer simulations.

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}
